---
title: 'A Tidyverse Approach to Alpha, Beta and Gamma Diversities'
subtitle: 'Computed and Visualized Using Formulas and Using the Package `vegetarian`'
author: 'Amir Barghi'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Formulas

For the formulas used in this file, see the following articles:

- L. Jost, "Entropy and diversity", *Oikos*, vol. 113, pp. 363--375, Jan. 2006.
- L. Jost, "Partitioning diversity into independent alpha and beta components", *Ecology*, vol. 88, pp. 2427--2439, Oct. 2008. 

# Loading Packages

```{r, message = FALSE}
library(vegetarian)

library(tidyverse)

library(latex2exp)
```

```{r}
# about the vegetarian package
?vegetarian
```

# Loading the Data Set `vegetarian::simesants`

```{r}
data(simesants)
```

```{r}
df <- simesants
```

# Tidying the Data Set

```{r}
# adding a new column `Weight`
# `Weight` is the proportion of the total population in each `Habitat`
df <- df %>% 
  rowwise() %>% 
  mutate(Count = sum(c_across(where(is.numeric)))) %>%
  ungroup()

df <- df %>% 
  mutate(Total_Count = sum(Count))

df <- df %>% 
  mutate(Weight = Count / Total_Count)

df <- df %>% 
  select(Habitat, Weight, everything(), -Count, -Total_Count)

df
```

```{r}
var_names <- df %>% 
  select(-Habitat, -Weight) %>% names() 

DF <- df %>% 
  gather(all_of(var_names), key = 'Species', value = 'Count') %>% 
  filter(Count > 0) %>%
  select(Habitat, Species, everything())

DF # gathered data set, with zero counts removed
```

```{r}
# number of habitats or communities
N <- DF %>% select(Habitat) %>% unique() %>% nrow()
```

# Gamma Diversities 

### Unweighted Gamma Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
giml_df <- DF %>% 
  group_by(Habitat) %>% 
  mutate(Habitat_Pop = sum(Count)) %>% 
  ungroup()

giml_u_m <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop, 
         Weight = 1 / N)

giml_u_m <- giml_u_m %>% 
  select(-Habitat) %>%
  group_by(Species) %>%
  mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
  ungroup() %>%
  select(Species, Weighted_Prop) %>%
  unique()

giml_u_m <- giml_u_m %>% 
  summarise(Gamma_Richness = n(),
            Gamma_Shannon = exp(-sum(Weighted_Prop * log(Weighted_Prop))),
            Gamma_Greenberg = 1 / sum(Weighted_Prop ** 2))

giml_u_m

giml_u_v <- df %>% 
  summarise(Gamma_Richness = d(.[, -c(1, 2)], lev = 'gamma', q = 0), 
            Gamma_Shannon = d(.[, -c(1, 2)], lev = 'gamma', q = 1), 
            Gamma_Greenberg = d(.[, -c(1, 2)], lev = 'gamma', q = 2))

giml_u_v
```

### Weighted Gamma Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
giml_w_m <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop, 
         Weight = Habitat_Pop / Total_Pop)

giml_w_m <- giml_w_m %>%  
  select(-Habitat) %>%
  group_by(Species) %>%
  mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
  ungroup() %>%
  select(Species, Weighted_Prop) %>%
  unique()

giml_w_m <- giml_w_m %>% 
  summarise(Gamma_Richness = n(),
            Gamma_Shannon = exp(-sum(Weighted_Prop * log(Weighted_Prop))),
            Gamma_Greenberg = 1 / sum(Weighted_Prop ** 2))

giml_w_m

giml_w_v <- df %>% 
  summarise(Gamma_Richness = d(.[, -c(1, 2)], lev = 'gamma', wt = .$Weight, q = 0),
            Gamma_Shannon = d(.[, -c(1, 2)], lev = 'gamma', wt = .$Weight, q = 1),
            Gamma_Greenberg = d(.[, -c(1, 2)], lev = 'gamma', wt = .$Weight, q = 2))

giml_w_v
```

# Alpha Diversities 

### Unweighted Alpha Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
alep_df <- DF %>% mutate(Total_Pop = sum(Count))

alep_u_m <- alep_df %>% 
  group_by(Habitat) %>% 
  mutate(Pop = sum(Count), 
         Prop = Count / Pop,
         Total_Prop = Count / Total_Pop,
         Weight = 1 / N)

suppressMessages(alep_u_m <- alep_u_m %>% 
                   summarise(Richness = n(), 
                             Shannon = -sum(Prop * log(Prop)),
                             Greenberg = sum(Prop ** 2)) %>%
                   ungroup() %>% 
                   unique())

alep_u_m <- alep_u_m %>% 
  summarise(Alpha_Richness = mean(Richness), 
            Alpha_Shannon = exp(mean(Shannon)), 
            Alpha_Greenberg = 1 / mean(Greenberg))

alep_u_m

alep_u_v <- df %>% 
  summarise(Alpha_Richness = d(.[, -c(1, 2)], lev = 'alpha', q = 0), 
            Alpha_Shannon = d(.[, -c(1, 2)], lev = 'alpha', q = 1), 
            Alpha_Greenberg = d(.[, -c(1, 2)], lev = 'alpha', q = 2))

alep_u_v
```

### Weighted Alpha Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
alep_df <- DF %>% mutate(Total_Pop = sum(Count))

alep_w_m <- alep_df %>% 
  group_by(Habitat) %>% 
  mutate(Habitat_Pop = sum(Count), 
         Prop = Count / Habitat_Pop,
         Weight = Habitat_Pop / Total_Pop,
         Richness = n(),
         Shannon = -sum(Prop * log(Prop)),
         Greenberg = sum(Prop ** 2)) %>%
  ungroup() %>%
  select(Habitat, 
         Richness, 
         Shannon, 
         Greenberg, 
         Habitat_Pop, 
         Total_Pop, 
         Weight) %>%
  unique()
        
suppressMessages(alep_w_m <- alep_w_m %>% 
                   summarise(Alpha_Richness = mean(Richness),
                             Alpha_Shannon = exp(sum(Shannon * Weight)),
                             Alpha_Greenberg = sum(Weight ** 2) / sum(Weight ** 2 * Greenberg )))

alep_w_m

alep_w_v <- df %>% 
  summarise(Alpha_Richness = d(.[, -c(1, 2)], lev = 'alpha', wt = .$Weight, q = 0), 
            Alpha_Shannon = d(.[, -c(1, 2)], lev = 'alpha', wt = .$Weight, q = 1),
            Alpha_Greenberg = d(.[, -c(1, 2)], lev = 'alpha', wt = .$Weight, q = 2))

alep_w_v
```

# Beta Diversities 

### Unweighted Beta Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
bet_u_m <- giml_u_m / alep_u_m 

names(bet_u_m) <- c('Beta_Richness', 'Beta_Shannon', 'Beta_Greenberg')

bet_u_v <- giml_u_v / alep_u_v

names(bet_u_v) <- c('Beta_Richness', 'Beta_Shannon', 'Beta_Greenberg')

bet_u_m

bet_u_v
```

```{r}
# alternatively
beta_u_v <- df %>% 
  summarise(Beta_Richness = d(.[, -c(1, 2)], lev = 'beta', q = 0), 
            Beta_Shannon = d(.[, -c(1, 2)], lev = 'beta', q = 1), 
            Beta_Greenberg = d(.[, -c(1, 2)], lev = 'beta', q = 2))

beta_u_v
```

### Weighted Beta Diversities Computed Using Fromulas and Using `vegetarian::d`

```{r}
bet_w_m <- giml_w_m / alep_w_m

names(bet_w_m) <- c('Beta_Richness', 'Beta_Shannon', 'Beta_Greenberg')

bet_w_v <- giml_w_v / alep_w_v

names(bet_w_v) <- c('Beta_Richness', 'Beta_Shannon', 'Beta_Greenberg')

bet_w_m

bet_w_v
```

```{r}
# alternatively
beta_u_v <- df %>% 
  summarise(Beta_Richness = d(.[, -c(1, 2)], lev = 'beta', wt = .$Weight, q = 0), 
            Beta_Shannon = d(.[, -c(1, 2)], lev = 'beta', wt = .$Weight, q = 1), 
            Beta_Greenberg = d(.[, -c(1, 2)], lev = 'beta', wt = .$Weight, q = 2))

beta_u_v
```

# Visualizing Diversities

```{r}
# defining two ranges: (0, 1) and (1, 10)
range_1 <- seq(0.001, 1, .01)

range_2 <- seq(1.001, 5, .01)
```

### Visualizing Unweighted Gamma Diversity Computed Using Fromulas 

```{r}
qsum1_g_u_m <- NULL

giml <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop, 
         Weight = 1 / N)

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- giml %>%  
      select(-Habitat) %>%
      group_by(Species) %>%
      mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
      ungroup() %>%
      select(Species, Weighted_Prop) %>%
      unique()
    
    df2 <- df2 %>% 
      summarise(Giml_Manual = sum(Weighted_Prop ** q) ** (1/ (1 - q)), 
                q = q)
    
    qsum1_g_u_m <- rbind(qsum1_g_u_m, df2)
    
}

print(qsum1_g_u_m %>% 
        ggplot(aes(x = q, y = Giml_Manual)) + 
        geom_line( color = 'blue') +
        geom_hline(yintercept = giml_u_m$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_u_m$Gamma_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color= 'yellow') + 
        labs(title = 'Unweighted Gamma Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

```{r}
qsum2_g_u_m <- NULL

giml <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop,
         Weight = 1 / N)

for (q in range_2) {
  
    df2 <- NULL
    
    df2 <- giml %>%  
      select(-Habitat) %>%
      group_by(Species) %>%
      mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
      ungroup() %>%
      select(Species, Weighted_Prop) %>%
      unique()
    
    df2 <- df2 %>% 
      summarise(Giml_Manual = sum(Weighted_Prop ** q) ** (1 / (1 - q)),
                q = q)
    
    qsum2_g_u_m <- rbind(qsum2_g_u_m, df2)
    
}

print(qsum2_g_u_m %>% 
        ggplot(aes(x = q, y = Giml_Manual)) + 
        geom_line( color = 'blue') +
        geom_hline(yintercept = giml_u_m$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_u_m$Gamma_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color= 'yellow') + 
        labs(title = 'Unweighted Gamma Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

### Visualizing Weighted Gamma Diversity Computed Using Fromulas

```{r}
qsum1_g_w_m <- NULL

giml <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop, 
         Weight = Habitat_Pop / Total_Pop)

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- giml %>%  
      select(-Habitat) %>%
      group_by(Species) %>%
      mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
      ungroup() %>%
      select(Species, Weighted_Prop) %>%
      unique()
    
    df2 <- df2 %>% 
      summarise(Giml_Manual = sum(Weighted_Prop ** q) ** (1/ (1 - q)), 
                q = q)
    
    qsum1_g_w_m <- rbind(qsum1_g_w_m, df2)
    
}

print(qsum1_g_w_m %>% 
        ggplot(aes(x = q, y = Giml_Manual)) + 
        geom_line( color = 'blue') +
        geom_hline(yintercept = giml_w_m$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_w_m$Gamma_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color= 'yellow') + 
        labs(title = 'Weighted Gamma Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

```{r}
qsum2_g_w_m <- NULL

giml <- giml_df %>% 
  mutate(Total_Pop = sum(Count), 
         Prop = Count / Habitat_Pop, 
         Weight = Habitat_Pop / Total_Pop)

for (q in range_2) {
  
    df2 <- NULL
    
    df2 <- giml %>%  
      select(-Habitat) %>%
      group_by(Species) %>%
      mutate(Weighted_Prop = sum(Prop * Weight)) %>% 
      ungroup() %>%
      select(Species, Weighted_Prop) %>%
      unique()
    
    df2 <- df2 %>% 
      summarise(Giml_Manual = sum(Weighted_Prop ** q) ** (1 / (1 - q)),
                q = q)
    
    qsum2_g_w_m <- rbind(qsum2_g_w_m, df2)
    
}

print(qsum2_g_w_m %>% 
        ggplot(aes(x = q, y = Giml_Manual)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = giml_w_m$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_w_m$Gamma_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color= 'yellow') + 
        labs(title = 'Weighted Gamma Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

### Visualizing Unweighted Gamma Diversity Computed Using `vegetarian::d`

```{r}
qsum1_g_u_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'gamma', wt = 1 / N, q = q), q = q)
    
    names(df2) <- c('Giml_Vegetarian', 'q')
    
    qsum1_g_u_v <- rbind(qsum1_g_u_v, df2)
    
}

print(qsum1_g_u_v %>% 
        ggplot(aes(x = q, y = Giml_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = giml_u_v$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_u_v$Gamma_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color= 'yellow') + 
        labs(title = 'Unweighted Gamma Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

```{r}
qsum2_g_u_v <- NULL

for (q in range_2) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'gamma', wt = 1 / N, q = q), q = q)
    
    names(df2) <- c('Giml_Vegetarian', 'q')
    
    qsum2_g_u_v <- rbind(qsum2_g_u_v, df2)
    
}

print(qsum2_g_u_v %>% 
        ggplot(aes(x = q, y = Giml_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = giml_u_v$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_u_v$Gamma_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color= 'yellow') + 
        labs(title = 'Unweighted Gamma Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

### Visualizing Weighted Gamma Diversity Computed Using `vegetarian::d`

```{r}
qsum1_g_w_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'gamma', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Giml_Vegetarian', 'q')
    
    qsum1_g_w_v <- rbind(qsum1_g_w_v, df2)
    
}

print(qsum1_g_w_v %>% 
        ggplot(aes(x = q, y = Giml_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = giml_w_v$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_w_v$Gamma_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color= 'yellow') + 
        labs(title = 'Weighted Gamma Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

```{r}
qsum2_g_w_v <- NULL

for (q in range_2) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'gamma', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Giml_Vegetarian', 'q')
    
    qsum2_g_w_v <- rbind(qsum2_g_w_v, df2)
    
}

print(qsum2_g_w_v %>% 
        ggplot(aes(x = q, y = Giml_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = giml_w_v$Gamma_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = giml_w_v$Gamma_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color= 'yellow') + 
        labs(title = 'Weighted Gamma Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\gamma$ Diversity'))) 
```

```{r}
alep <- DF %>% mutate(Total_Pop = sum(Count))
```

### Visualizing Unweighted Alpha Diversity Computed Using Fromulas 

```{r}
qsum1_a_u_m <- NULL

for (q in range_1) {
  
    df2 <- NULL

    df2 <- alep %>%
      group_by(Habitat) %>% 
      mutate(Habitat_Pop = sum(Count), 
             Prop = Count / Habitat_Pop,
             Weight = 1 / N,
             Smallqsum = sum((Prop * Weight) ** q),
             q = q) %>%
      ungroup() %>%
      select(Habitat, Smallqsum, Weight, q) %>%
      unique()
    
    suppressMessages(df2 <- df2 %>% 
                       group_by(q) %>% 
                       summarise(Alep_Manual = (sum(Smallqsum) / sum(Weight ** q)) ** (1 / (1 - q)), 
                                 q = q))
    
    qsum1_a_u_m <- rbind(qsum1_a_u_m, df2)
    
}

print(qsum1_a_u_m %>% 
        ggplot(aes(x = q, y = Alep_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_u_m$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_u_m$Alpha_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Unweighted Alpha Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
qsum2_a_u_m <- NULL

for (q in range_2) {
    
    df2 <- NULL
    
    df2 <- alep %>%
      group_by(Habitat) %>% 
      mutate(Habitat_Pop = sum(Count), 
             Prop = Count / Habitat_Pop,
             Weight = 1 / N,
             Smallqsum = sum((Prop * Weight) ** q),
             q = q) %>%
      ungroup() %>%
      select(Habitat, Smallqsum, Weight, q) %>%
      unique()
    
    suppressMessages(df2 <- df2 %>% 
                       group_by(q) %>% 
                       summarise(Alep_Manual = (sum(Smallqsum) / sum(Weight ** q)) ** (1 / (1 - q)), 
                                 q = q))
    
    qsum2_a_u_m <- rbind(qsum2_a_u_m, df2)
}

print(qsum2_a_u_m %>% 
        ggplot(aes(x = q, y = Alep_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_u_m$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_u_m$Alpha_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Unweighted Alpha Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity')))  
```

### Visualizing Weighted Alpha Diversity Computed Using Fromulas 

```{r}
qsum1_a_w_m <- NULL

for (q in range_1) {
  
    df2 <- NULL

    df2 <- alep %>%
      group_by(Habitat) %>% 
      mutate(Habitat_Pop = sum(Count), 
             Prop = Count / Habitat_Pop,
             Weight = Habitat_Pop / Total_Pop,
             Smallqsum = sum((Prop * Weight) ** q),
             q = q) %>%
      ungroup() %>%
      select(Habitat, Smallqsum, Weight, q) %>%
      unique()
    
    suppressMessages(df2 <- df2 %>% 
                       group_by(q) %>% 
                       summarise(Alep_Manual = (sum(Smallqsum) / sum(Weight ** q)) ** (1 / (1 - q)), 
                                 q = q))
    
    qsum1_a_w_m <- rbind(qsum1_a_w_m, df2)
    
}

print(qsum1_a_w_m %>% 
        ggplot(aes(x = q, y = Alep_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_w_m$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_w_m$Alpha_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Alpha Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
qsum2_a_w_m <- NULL

for (q in range_2) {
    
    df2 <- NULL
    
    df2 <- alep %>%
      group_by(Habitat) %>% 
      mutate(Habitat_Pop = sum(Count), 
             Prop = Count / Habitat_Pop,
             Weight = Habitat_Pop / Total_Pop,
             Smallqsum = sum((Prop * Weight) ** q),
             q = q) %>%
      ungroup() %>%
      select(Habitat, Smallqsum, Weight, q) %>%
      unique()
    
    suppressMessages(df2 <- df2 %>% 
                       group_by(q) %>% 
                       summarise(Alep_Manual = (sum(Smallqsum) / sum(Weight ** q)) ** (1 / (1 - q)), 
                                 q = q))
    
    qsum2_a_w_m <- rbind(qsum2_a_w_m, df2)
    
}

print(qsum2_a_w_m %>% 
        ggplot(aes(x = q, y = Alep_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_w_m$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_w_m$Alpha_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Alpha Diversity Computed Using Fromulas ') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity')))  
```

### Visualizing Unweighted Alpha Diversity Computed Using `vegetarian::d`

```{r}
qsum1_a_u_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'alpha', q = q), q = q)
    
    names(df2) <- c('Alep_Vegetarian', 'q')
    
    qsum1_a_u_v <- rbind(qsum1_a_u_v, df2)
    
}

print(qsum1_a_u_v %>% 
        ggplot(aes(x = q, y = Alep_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = alep_u_v$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = alep_u_v$Alpha_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color= 'yellow') + 
        labs(title = 'Unweighted Alpha Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
qsum2_a_u_v <- NULL

for (q in range_2) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'alpha', q = q), q = q)
    
    names(df2) <- c('Alep_Vegetarian', 'q')
    
    qsum2_a_u_v <- rbind(qsum2_a_u_v, df2)
    
}

print(qsum2_a_u_v %>% 
        ggplot(aes(x = q, y = Alep_Vegetarian)) + 
        geom_line(color = 'blue') +
        geom_hline(yintercept = alep_u_v$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color= 'green') + 
        geom_hline(yintercept = alep_u_v$Alpha_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color= 'yellow') + 
        labs(title = 'Unweighted Alpha Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

### Visualizing Weighted Alpha Diversity Computed Using `vegetarian::d``

```{r}
qsum1_a_w_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'alpha', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Alep_Vegetarian', 'q')
    
    qsum1_a_w_v <- rbind(qsum1_a_w_v, df2)
    
}

print(qsum1_a_w_v %>% 
        ggplot(aes(x = q, y = Alep_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_w_v$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_w_v$Alpha_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Alpha Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
qsum2_a_w_v <- NULL

for (q in range_2) {
    
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'alpha', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Alep_Vegetarian', 'q')
    
    qsum2_a_w_v <- rbind(qsum2_a_w_v, df2)
    
}

print(qsum2_a_w_v %>% 
        ggplot(aes(x = q, y = Alep_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = alep_w_v$Alpha_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = alep_w_v$Alpha_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Alpha Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity')))  
```

### Visualizing Unweighted Beta Diversity Computed Using Fromulas 

```{r}
qsum1_b_u_m <- inner_join(qsum1_g_u_m, qsum1_a_u_m, by = 'q')

qsum1_b_u_m <- qsum1_b_u_m %>% mutate(Bet_Manual = Giml_Manual / Alep_Manual)

print(qsum1_b_u_m %>%
        ggplot(aes(x = q, y = Bet_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_m$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_m$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Unweighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
qsum2_b_u_m <- inner_join(qsum2_g_u_m, qsum2_a_u_m, by = 'q')

qsum2_b_u_m <- qsum2_b_u_m %>% mutate(Bet_Manual = Giml_Manual / Alep_Manual)

print(qsum2_b_u_m %>% 
        ggplot(aes(x = q, y = Bet_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_m$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_m$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Unweighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
# alternatively
qsum1_b_u_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'beta', q = q), q = q)
    
    names(df2) <- c('Bet_Vegetarian', 'q')
    
    qsum1_b_u_v <- rbind(qsum1_b_u_v, df2)
    
}

print(qsum1_b_u_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_v$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Alpha Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
# alternatively
qsum2_b_u_v <- NULL

for (q in range_2) {
    
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'beta', q = q), q = q)
    
    names(df2) <- c('Bet_Vegetarian', 'q')
    
    qsum2_b_u_v <- rbind(qsum2_b_u_v, df2)
    
}

print(qsum2_b_u_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_v$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

### Visualizing Weighted Beta Diversity Computed Using Fromulas 

```{r}
qsum1_b_w_m <- inner_join(qsum1_g_w_m, qsum1_a_w_m, by = 'q')

qsum1_b_w_m <- qsum1_b_w_m %>% mutate(Bet_Manual = Giml_Manual / Alep_Manual)

print(qsum1_b_w_m %>% 
        ggplot(aes(x = q, y = Bet_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_m$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_m$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
qsum2_b_w_m <- inner_join(qsum2_g_w_m, qsum2_a_w_m, by = 'q')

qsum2_b_w_m <- qsum2_b_w_m %>% mutate(Bet_Manual = Giml_Manual / Alep_Manual)

print(qsum2_b_w_m %>% 
        ggplot(aes(x = q, y = Bet_Manual)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_m$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_m$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

### Visualizing Unweighted Beta Diversity Computed Using `vegetarian::d` 

```{r}
qsum1_b_u_v <- inner_join(qsum1_g_u_v, qsum1_a_u_v, by = 'q')

qsum1_b_u_v <- qsum1_b_u_v %>% mutate(Bet_Vegetarian = Giml_Vegetarian / Alep_Vegetarian)

print(qsum1_b_u_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_v$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Unweighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
qsum2_b_u_v <- inner_join(qsum2_g_u_v, qsum2_a_u_v, by = 'q')

qsum2_b_u_v <- qsum2_b_u_v %>% mutate(Bet_Vegetarian = Giml_Vegetarian / Alep_Vegetarian)

print(qsum2_b_u_v %>%
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_u_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_u_v$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Unweighted Beta Diversity Computed Using Fromulas') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

### Visualizing Weighted Beta Diversity Computed Using `vegetarian::d`

```{r}
qsum1_b_w_v <- inner_join(qsum1_g_w_v, qsum1_a_w_v, by = 'q')

qsum1_b_w_v <- qsum1_b_w_v %>% mutate(Bet_Vegetarian = Giml_Vegetarian / Alep_Vegetarian)

print(qsum1_b_w_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_v$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using `vegetarian::d`') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
qsum2_b_w_v <- inner_join(qsum2_g_w_v, qsum2_a_w_v, by = 'q')

qsum2_b_w_v <- qsum2_b_w_v %>% mutate(Bet_Vegetarian = Giml_Vegetarian / Alep_Vegetarian)

print(qsum2_b_w_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_v$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```

```{r}
# alternatively
qsum1_b_w_v <- NULL

for (q in range_1) {
  
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'beta', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Bet_Vegetarian', 'q')
    
    qsum1_b_w_v <- rbind(qsum1_b_w_v, df2)
    
}

print(qsum1_b_w_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_v$Beta_Richness, color = 'yellow') +
        geom_vline(xintercept = 0, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\alpha$ Diversity'))) 
```

```{r}
# alternatively
qsum2_b_w_v <- NULL

for (q in range_2) {
    
    df2 <- NULL
    
    df2 <- data.frame(d(df[, -c(1, 2)], lev = 'beta', wt = df$Weight, q = q), q = q)
    
    names(df2) <- c('Bet_Vegetarian', 'q')
    
    qsum2_b_w_v <- rbind(qsum2_b_w_v, df2)
    
}

print(qsum2_b_w_v %>% 
        ggplot(aes(x = q, y = Bet_Vegetarian)) + 
        geom_line( color = 'blue') + 
        geom_hline(yintercept = bet_w_v$Beta_Shannon, color = 'green') +
        geom_vline(xintercept = 1, color = 'green') + 
        geom_hline(yintercept = bet_w_v$Beta_Greenberg, color = 'yellow') +
        geom_vline(xintercept = 2, color = 'yellow') + 
        labs(title = 'Weighted Beta Diversity Computed Using vegetarian::d') +
        xlab(TeX('$q$')) +
        ylab(TeX('$\\beta$ Diversity')))  
```